Quantum Interval-Valued Probability: Measurement and Probability

### 2017-08-24 prop_iop.tex
prop_iop.tex \subsection{Expectation Values for Classical IVPMs} Add more lemmas...

>>>>

Finally, we are going to focus on CIVPMs whose range is $\mathscr{I}_{\mathrm{D}}$.

\begin{lemma}\label{lemma:deterministic-CIVPM}Given a CIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
the following statements are true:
\begin{enumerate}
\item Its left-end~$\mul$ and right-end~$\mur$ are the same CRVPM, and
will be simply denoted by $\pmeas:\events\rightarrow\left\{ 1,0\right\} $
\item There is a unique $\omega_{0}\in\Omega$ such that $\bar{\mu}\left(\left\{ \omega_{0}\right\} \right)=\left\{ \pmeas\left(\left\{ \omega_{0}\right\} \right)\right\} =\necess$,
denoted by $\pmeas^{-1}\left(1\right)$ or $\bar{\mu}^{-1}\left(\necess\right)$.
\end{enumerate}
\end{lemma}

\begin{proof}~
\begin{enumerate}
\item The directly consequence of lemma~\ref{lemma:QIVPM2QCM}.
\item Since the range of $\pmeas$ is $\left\{ 1,0\right\} $ and $\sum_{\omega\in\Omega}\pmeas\left(\left\{ \omega\right\} \right)=1$,
there is a unique $\omega_{0}$ such that $\mu\left(\left\{ \omega_{0}\right\} \right)=1$
which implies $\bar{\mu}\left(\left\{ \omega_{0}\right\} \right)=\necess$.
\end{enumerate}
\end{proof}

\begin{lemma}\label{lemma:deterministic-CIVPM-expectation}For any
CIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$ and
a random variable~$X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{E_{i}}$, then
$\int X\rmd\bar{\mu}=\left\{ X\left(\bar{\mu}^{-1}\left(\necess\right)\right)\right\} $.\end{lemma}

\begin{proof}By adopting the notation in lemma~\ref{lemma:deterministic-CIVPM},
we have
\begin{equation}
\int X\rmd\bar{\mu}\stackrel{\textrm{Lemma }\ref{lemma:Choquet-Lebesgue}}{=}\left\{ \int X\rmd\mu\right\} \stackrel{\textrm{Equation }(\ref{eq:expectation})}{=}\left\{ X\left(\pmeas^{-1}\left(1\right)\right)\cdot1\right\} =\left\{ X\left(\bar{\mu}^{-1}\left(\necess\right)\right)\right\} \,.\label{eq:expectation-value-eigenvalue-classical}
\end{equation}
\end{proof}

Given two singleton sets~$\left\{ x_{1}\right\} $ and $\left\{ x_{2}\right\} $,
it is intuitive to define their multiplication of to be $\left\{ x_{1}x_{2}\right\} $
which gives the following lemma.

\begin{lemma}For any CIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$
and a sequence of random variable~$\left\{ X_{j}\right\} $,
\begin{equation}
\prod_{j}\int X_{j}\rmd\bar{\mu}=\int\prod_{j}X_{j}\rmd\bar{\mu}\,.\label{eq:Kochen-Specker-Rules-classical}
\end{equation}
\end{lemma}

\begin{proof} 
\begin{equation}
\prod_{j}\int X_{j}\rmd\bar{\mu}\stackrel{\textrm{Lemma }\ref{lemma:deterministic-CIVPM-expectation}}{=}\prod_{j}\left\{ X_{j}\left(\bar{\mu}^{-1}\left(\necess\right)\right)\right\} =\left\{ \prod_{j}X_{j}\left(\bar{\mu}^{-1}\left(\necess\right)\right)\right\} \stackrel{\textrm{Lemma }\ref{lemma:deterministic-CIVPM-expectation}}{=}\int\prod_{j}X_{j}\rmd\bar{\mu}\,.\label{eq:expectation-value-eigenvalue-classical-1}
\end{equation}
\end{proof}
